Estimation of flow trajectories in a multi-lines transportation network

### 2023-02-21 latex_files/applied_network_science_article/article_v0.tex
toy results

All constructed toy examples are built following the same approach, which aims at being simple but somewhat realistic. We fix a number of \emph{line tours} $p \geq 2$, each of which is constituted of a forward line and a backward line, for a total of $q = 2p$ lines. Every line has a starting and ending node, which are isolated node, and posses $p-1$ intermediary nodes which allows transfers to the other tour lines, giving a total of $n = 2p(p + 1)$ nodes in the network. Examples of these toy networks can be found in Figure \ref{toy_example_plots}.

@@

>>>>

All constructed toy examples are built following the same approach, which aims at being simple but somewhat realistic. We fix a number of \emph{line tours} $p \geq 2$, each of which is constituted of a forward line and a backward line, for a total of $q = 2p$ lines. Every line has a starting and ending node, which are isolated nodes, and posses $p-1$ intermediary nodes which allows transfers to the other tour lines, giving a total of $n = 2p(p + 1)$ nodes in the network. Examples of these toy networks can be found in Figure \ref{toy_example_plots}.

@@

\begin{figure}
	\includegraphics[width=0.47\textwidth]{fig/toy_MTE_passengers_theta01.pdf}
	\includegraphics[width=0.47\textwidth]{fig/toy_MTE_tours.pdf}
	\caption{\emph{Mean transportation error} (MTE), according to the number of tours $p \in \{2,3,4,5,6,7,8\}$ and resp. to the number of passengers into the network per line tour and the minimum proportion $\theta =0.1$ of passengers entering/leaving the network at each stop with a proportional number of passengers to the shortest paths of each line tour.}
	\label{toy_MTE}
\end{figure}

By running the algorithm for line tours $p \in \{2,3,4,5,6,7,8\}$, we observe that MTE depends on different parameters. On the graph on the left in Figure \ref{toy_MTE}, the number of passengers inserted in the network has an influence on MTE. The higher the number of passengers, the smaller the error is because passengers are better distributed throughout the larger network. On the right in Figure \ref{toy_MTE}, the aim is to understand how the proportion $\theta\in (0,1)$ responds to different line tours. Dots represent local minimum MTE for each tour.
